### 2013-07-31 doc/cover_letter.tex
a few changes before submission to plos, submission to plosone done

\usepackage{color}

@@

% Text layout
\topmargin 0.0cm
\oddsidemargin 1cm
\evensidemargin 1cm
% \textwidth 16cm 
% \textheight 21cm

@@

Please find enclosed the manuscript “taxize: taxonomic search and retrieval in R” that we are re-submitting for publication as an article to PLOS One.

Our manuscript is an excellent candidate for PLOS One because it describes a \emph{taxonomic toolbelt} in the form of new open source software for the R programming language. Taxonomy is likely used by all biologists, whether they look up the sister species of their single study species for a new experiment, or use taxonomy as the basis for creating phylogenetic trees. XXXXXX. Previous software and papers discussing the software include X, Y, and Z. Those software packages perform different tasks than our software. Our software is targeted at the most widely used statistical programming language, R, that many scientists already use. We aim to bring a taxonomic toolkit to scientists working in R. The previous works in this area (X, Y, and Z) XXXX.

We are submitting this manuscript as a Research article. There has been no prior interaction with PLOS with respect to this manuscript. This manuscript has benefited from the comments of Carl Boettiger, Karthik Ram, Owen Jones, Naim Matasci, and Ralf Sch\"{a}fer. The material presented in this manuscript has not been published previously, nor is it under consideration for publication elsewhere. The authors have no professional or financial affiliations that bias this publication.

Thank you for considering our work for publication in PLOS One.

Sincerely yours,

Scott Chamberlain

Eduard Sz\"{o}cs

* Corresponding Author: 
Scott Chamberlain, Department of Biology Simon Fraser University Burnaby, BC, Canada

>>>>

\usepackage[margin=1in]{geometry}
\usepackage{color}

@@

% Text layout
% \topmargin 0.0cm
% \oddsidemargin 0.75cm
% \evensidemargin 0.75cm
% \textwidth 16cm

@@

Please find enclosed the manuscript \emph{taxize: taxonomic search and retrieval in R} that we are re-submitting for publication as an article to PLOS One.

Our manuscript is an excellent candidate for PLOS One because it describes a \emph{taxonomic toolbelt} in the form of new open source software for the R programming language. Taxonomy is likely used by all biologists, whether they look up the sister species of their single study species for a new experiment, or use taxonomy as the basis for creating phylogenetic trees. taxize interacts with a large suite of databases online to connect researchers to taxonomic data. This is extremely important as taxize allows researchers to validate species names, look up synonyms, get higher taxonomic names, and more, all within their data analysis workflow in R - which ultimately makes for more reproducible science. Previous software and papers discussing similar software include desktop software (Linnaeus, OrganismTagger), and web based tools (Encyclopedia of Life, Integrated Taxonomic Information Service, and more). However, the desktop applications mentioned, and those not mentioned, are GUI environments - thus, do not plug in to existing workflows for scientists.  The web tools mentioned, and those not mentioned, are largely accessible by taxize. In addition, accessing data through a web interface is not ideal as it is not reproducible, and gets very time consuming for large tasks. Our software is targeted at the most widely used statistical programming language, R, that many scientists already use. We aim to bring a taxonomic toolkit to scientists working in R.

We are submitting this manuscript as a Research article. There has been no prior interaction with PLOS with respect to this manuscript. This manuscript has benefited from the comments of Carl Boettiger, Karthik Ram, Owen Jones, Naim Matasci, and Ralf Sch\"{a}fer. The material presented in this manuscript has not been published previously, nor is it under consideration for publication elsewhere. The authors have no professional or financial affiliations that bias this publication. Thank you for considering our work for publication in PLOS One.

\flushleft
Sincerely yours,

Scott Chamberlain and Eduard Sz\"{o}cs
\endflushleft

### 2013-07-31 doc/taxize_withcode_app.Rnw
a few changes before submission to plos, submission to plosone done

\begin{document}
<<setup, include=FALSE, cache=FALSE>>=
## set global chunk options
opts_chunk$set(fig.path='figure/', fig.align='center', fig.show='hold', par=TRUE, warning=FALSE, message=FALSE, error=FALSE, comment=NA)
@

\begin{appendices}
<<appA, child='taxize_withcode_appA.Rnw', eval=TRUE>>=
@

\newpage
<<appB, child='taxize_withcode_appB.Rnw', eval=TRUE>>=
@
\end{appendices}

>>>>

\begin{document}
<<setup, include=FALSE, cache=FALSE>>=
opts_chunk$set(fig.align='center', fig.show='hold', par=TRUE, warning=FALSE, message=FALSE, error=FALSE, comment=NA)
@

\begin{appendices}
<<appA, child='taxize_withcode_appA.Rnw', eval=TRUE, fig.path='figure/'>>=
@

\newpage
<<appB, child='taxize_withcode_appB.Rnw', eval=TRUE, fig.path='figure/'>>=
@
\end{appendices}

### 2013-07-31 doc/taxize_withcode_app.tex
a few changes before submission to plos, submission to plosone done

\documentclass[letterpaper,superscriptaddress,showkeys,longbibliography,10pt]{revtex4-1}\usepackage{graphicx, color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

@@

\hlcomment{# Remove some fields}
(splist_tnrs <- splist_tnrs[, !\hlfunctioncall{names}(splist_tnrs) %in% \hlfunctioncall{c}(\hlstring{"matchedName"}, \hlstring{"annotations"}, 
    \hlstring{"uri"})])
\end{alltt}
\begin{verbatim}
           submittedName         acceptedName    sourceId score
3       Helanthus annuus    Helianthus annuus iPlant_TNRS  0.98
1         Pinos contorta       Pinus contorta iPlant_TNRS  0.96
4  Collomia grandiflorra Collomia grandiflora iPlant_TNRS  0.99
5       Abies magnificaa      Abies magnifica iPlant_TNRS  0.98
10       Rosa california     Rosa californica iPlant_TNRS  0.99
9         Datura wrighti      Datura wrightii iPlant_TNRS  0.98
7       Mimulus bicolour      Mimulus bicolor iPlant_TNRS  0.98
8       Nicotiana glauca     Nicotiana glauca iPlant_TNRS  1.00
6          Maddia sativa         Madia sativa iPlant_TNRS  0.97
2    Bartlettia scapposa   Bartlettia scaposa iPlant_TNRS  0.98
\end{verbatim}
\begin{alltt}

@@

{\centering \includegraphics[width=4in,height=4in]{figure/phylogeny}

@@

\hlcomment{# Make a map}
p <- \hlfunctioncall{gbifmap}(occurr_list) + \hlfunctioncall{guides}(col = \hlfunctioncall{guide_legend}(title = \hlstring{""}, nrow = 3, 
    byrow = TRUE)) + \hlfunctioncall{theme}(legend.position = \hlstring{"bottom"}, legend.key = \hlfunctioncall{element_blank}()) + 
    \hlfunctioncall{coord_equal}()
p
\end{alltt}
\end{kframe}\begin{figure}[h]

{\centering \includegraphics[width=.9\textwidth]{figure/plot_map}

\caption[A map]{A map\label{fig:mapplot_map}}
\end{figure}

@@

\hlfunctioncall{require}(reshape2)
\hlcomment{# reshape data to long format and name rows by samples}
L <- \hlfunctioncall{dcast}(abundances, sample ~ traits_taxa, fun.aggregate = sum, value.var = \hlstring{"abundance"})
\hlfunctioncall{rownames}(L) <- L$sample
L$sample <- NULL
L
\end{alltt}
\begin{verbatim}
  coenagrionidae-aggregated gammarus potamopyrgus antipodarum
1                        10       12                       10
2                         6       14                        0
\end{verbatim}
\begin{alltt}

@@

This is just an example how taxonomic APIs (via taxize) could be used to search for matches up- and downwards the taxonomic ladder. We are looking forward to integrate the freshwaterecology.info database \citep{freshwaterecology} into taxize, which will facilitate trait-based analyses in R.

>>>>

\documentclass[letterpaper,superscriptaddress,showkeys,longbibliography,10pt]{revtex4-1}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

@@

\hlcomment{# Remove some fields}
(splist_tnrs <- splist_tnrs[, !\hlfunctioncall{names}(splist_tnrs) %in% \hlfunctioncall{c}(\hlstring{"matchedName"}, \hlstring{"annotations"}, 
    \hlstring{"uri"})])
\end{alltt}
\begin{verbatim}
           submittedName         acceptedName    sourceId score
3       Helanthus annuus    Helianthus annuus iPlant_TNRS  0.98
1         Pinos contorta       Pinus contorta iPlant_TNRS  0.96
4  Collomia grandiflorra Collomia grandiflora iPlant_TNRS  0.99
5       Abies magnificaa      Abies magnifica iPlant_TNRS  0.98
10       Rosa california     Rosa californica iPlant_TNRS  0.99
9         Datura wrighti      Datura wrightii iPlant_TNRS  0.98
7       Mimulus bicolour      Mimulus bicolor iPlant_TNRS  0.98
8       Nicotiana glauca     Nicotiana glauca iPlant_TNRS     1
6          Maddia sativa         Madia sativa iPlant_TNRS  0.97
2    Bartlettia scapposa   Bartlettia scaposa iPlant_TNRS  0.98
\end{verbatim}
\begin{alltt}

@@

{\centering \includegraphics[width=4in]{figure/phylogeny1.pdf} 
\includegraphics[width=4in]{figure/phylogeny2.pdf}

@@

\hlcomment{# Make a map}
p <- \hlfunctioncall{gbifmap}(occurr_list) + \hlfunctioncall{guides}(col = \hlfunctioncall{guide_legend}(title = \hlstring{""}, nrow = 3, 
    byrow = TRUE)) + \hlfunctioncall{theme}(legend.position = \hlstring{"bottom"}, legend.key = \hlfunctioncall{element_blank}()) + 
    \hlfunctioncall{coord_equal}()
p
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\hlfunctioncall{library}(reshape2)
\hlcomment{# reshape data to long format and name rows by samples}
L <- \hlfunctioncall{dcast}(abundances, sample ~ traits_taxa, fun.aggregate = sum, value.var = \hlstring{"abundance"})
\hlfunctioncall{rownames}(L) <- L$sample
L$sample <- NULL
L
\end{alltt}
\begin{verbatim}
  coenagrionidae-aggregated gammarus potamopyrgus antipodarum
1                        10       12                       10
2                         6       14                        0
\end{verbatim}
\begin{alltt}

@@

This is just an example how taxonomic APIs (via taxize) could be used to search for matches up- and downwards the taxonomic ladder. We are looking forward to integrate the freshwaterecology.info database \cite{freshwaterecology} into taxize, which will facilitate trait-based analyses in R.
